Thesis Title

### 2022-03-23 chapters/chapter_2.tex
add supplemental tables chapter 2

All the parameters used in each approach are available in Supplementary Table 1.

@@

\subsection{Accession codes}

@@

>>>>

All the parameters used in each approach are available in Supplementary Table 1 (see \ref{ch2_supmaterial}).

@@

\subsection{Accession codes} \label{ch2_supmaterial}

@@

\section{Supplemental Material}

\begin{table}[]
\caption{}
\label{tab:ch2_suptable1}
\resizebox{\textwidth}{!}{%
\begin{tabular}{ll}
\multicolumn{2}{c}{\textbf{FastQ Toolkit v2.2.0}}                                       \\
Minimum read length                             & 32                           \\
Sub-sampling                                    & FALSE                        \\
Adapter trim stringency                         & 0.9                          \\
Select respective adapters                      & TRUE                         \\
Quality trimming                                & FALSE                        \\
Poly-A/T Trimming                               & FALSE                        \\
Read Filtering                                  & FALSE                        \\
Modify Reads                                    & FALSE                        \\
Fix Format                                      & FALSE                        \\
\multicolumn{2}{c}{\textbf{FastQC v1.0.0}}                                              \\
Kmer Size                                       & 5                            \\
Use Conatminant Filter                          & TRUE                         \\
\multicolumn{2}{c}{\textbf{Kraken Metagenomics v1.0.0}}                                 \\
Host Filter                                     & TRUE RefSeqhg19              \\
Classification Database                         & MiniKraken 20141208 (latest) \\
Filter Threshold                                & 0                            \\
\multicolumn{2}{c}{\textbf{Metaphlan v1.0.0}}                                           \\
Sensitivity options for read-marker similarity (as descibed by BowTie2)                  & Very Sensitive \\
\multicolumn{2}{c}{\textbf{SPAdes Genome Assembler v3.9.0}}                             \\
Running Mode                                    & Error Correction \& Assembly \\
Dataset type                                    & Multi Cell                   \\
Careful Mode                                    & Disable                      \\
k-mer lengths                                   & Auto                         \\
\multicolumn{2}{c}{\textbf{SEAR: Antibiotic Resistance v1.0.0}}                                           \\
Read length cutoff (bases)                      & 70                           \\
Read quality score cutoff                       & 20                           \\
Read subtraction against E.coli reference genome (K12)?                                  & No             \\
Clustering stringency (express \% as a decimal) & 0.98                         \\
Annotation stringency (\% length of reference ARG sequence mapped to by sequencing reads & 40             \\
\multicolumn{2}{c}{\textbf{GENIUS Metagenomics: Know Now v1.1.0}}                                                  \\
Can't set any settings in BaseSpace             &                             
\end{tabular}%
}
\end{table}
\caption{}
\label{tab:ch2_suptable2}
\begin{tabular}{ll}
\multicolumn{2}{l}{Trim Reads}                                                          \\
Trimmomatic v0.36 (INNUca v2.6 initial module)     &                                    \\
Quality trim                                       & TRUE                               \\
Phred Quality limit                                & 05:20                              \\
Trim adapter list                                  & Illumina adapters                  \\
Remove 5' terminal nucleotides                     & TRUE                               \\
Number of 5' terminal nucleotides                  & 3                                  \\
Remove 3' terminal nucleotides                     & TRUE                               \\
Number of 3' terminal nucleotides                  & 3                                  \\
Discard short reads                                & TRUE                               \\
Minimum number of nucleotides in reads             & 55                                 \\
                                                   &                                    \\
\multicolumn{2}{l}{Map Reads to Reference}                                              \\
Bowtie2 v2.3.2                                     &                                    \\
References                                         & Homo sapiens (hg19) index          \\
Mode                                               & end-to-end                         \\
Mode option                                        & sensitive                          \\
Collect unmapped reads                             & FALSE                              \\
                                                   &                                    \\
\multicolumn{2}{l}{Taxonomic classification}                                            \\
Kraken v0.10.5-beta                                &                                    \\
References                                         & miniKraken database (Dec. 8, 2014) \\
K-mer length                                       & 35                                 \\
MIDAS                                              &                                    \\
References                                         & midas\_db\_v1.2 (May 9, 2018)      \\
Word size for blast                                & 28                                 \\
Alignment coverage                                 & 0.75                               \\
MetaPhlAn2 v2.0                                    &                                    \\
References                                         & default database (May 9, 2018)     \\
Minimum total nucleotide length for the markers    & 2000                               \\
Quantile value for robust average                  & 0.1                                \\
Statistical approach for converting marker abundances into clade abundances & clade global                                          \\
Analysis type                                                               & profiling a metagenome in terms of relative abundance \\
                                                   &                                    \\
\multicolumn{2}{l}{Identify MLST}                                                       \\
metaMLST v1.1                                      &                                    \\
References                                         & metamlstDB\_2017                   \\
Bowtie2 mode                                       & local                              \\
Bowtie2 mode option                                & very sensitive local               \\
Collect unmapped reads                             & FALSE                              \\
Search for and report all alignment                & TRUE                               \\
                                                   &                                    \\
\multicolumn{2}{l}{Find Resistance Genes}                                               \\
ReMatCh v3.2                                       &                                    \\
References                                         & ResFinder database (29-06-2017)    \\
Minimum coverage to consider a position as present & 1                                  \\
Minimum coverage depth to perform a basecall       & 1                                  \\
Minimum gene coverage (\%)                         & 80                                 \\
Minimum gene identity (\%)                         & 70                                 \\
                                                   &                                    \\
\multicolumn{2}{l}{De novo assembly}                                                    \\
SPAdes v3.10.1                                     &                                    \\
Mode                                               & careful                            \\
Error correction                                   & FALSE                              \\
Read coverage cut-off value                        & 2                                  \\
List of K-mers                                     & 21,33,55,67,77                     \\
                                                   &                                    \\
\multicolumn{2}{l}{Plasmid Detection}                                                   \\
Bowtie2 v2.3.2                                     &                                    \\
References                                         & NCBI RefSeq (May 11, 2017)         \\
Mode                                               & end-to-end                         \\
Mode option                                        & sensitive                          \\
Collect unmapped reads                             & FALSE                              \\
Multiple alignment                                 & TRUE                              

\newpage

\begin{longtable}{ll}
\caption{}
\label{tab:ch2_suptable3}\\
\multicolumn{2}{l}{Illumina}                                                                  \\
\endfirsthead
%
\endhead
%
Discard sequence names                       & FALSE                                          \\
Discard quality scores                       & FALSE                                          \\
Selected files                               &                                                \\
Paired-end reads                             & TRUE                                           \\
Read Orientation                             & Forward Reverse                                \\
minimum distance                             & 1                                              \\
maximum distance                             & 1000                                           \\
Remove failed reads                          & TRUE                                           \\
Quality score                                & NCBI/Sanger or Illumina Pipeline 1.8 and later \\
MiSeq de-multiplexing                        & FALSE                                          \\
Illumina trim                                & FALSE                                          \\
                                             &                                                \\
Trim Reads                                   &                                                \\
Quality trim                                 & TRUE                                           \\
Quality limit                                & 0.05                                           \\
Ambiguous trim                               & TRUE                                           \\
Ambiguous limit                              & 2                                              \\
Trim adapter list                            & Illumina adapters                              \\
Use colorspace                               & FALSE                                          \\
Remove 5' terminal nucleotides               & FALSE                                          \\
Number of 5' terminal nucleotides            & 1                                              \\
Remove 3' terminal nucleotides               & FALSE                                          \\
Number of 3' terminal nucleotides            & 1                                              \\
Discard short reads                          & TRUE                                           \\
Minimum number of nucleotides in reads       & 30                                             \\
Discard long reads                           & FALSE                                          \\
Maximum number of nucleotides in reads       & 1000                                           \\
                                             &                                                \\
Map Reads to Reference                       &                                                \\
References                                   & Homo sapiens (hg19) sequence                   \\
Masking mode                                 & No masking                                     \\
Masking track                                &                                                \\
Match score                                  & 1                                              \\
Mismatch cost                                & 2                                              \\
Cost of insertions and deletions             & Linear gap cost                                \\
Insertion cost                               & 3                                              \\
Deletion cost                                & 3                                              \\
Insertion open cost                          & 6                                              \\
Insertion extend cost                        & 1                                              \\
Deletion open cost                           & 6                                              \\
Deletion extend cost                         & 1                                              \\
Length fraction                              & 0.5                                            \\
Similarity fraction                          & 0.8                                            \\
Global alignment                             & FALSE                                          \\
Color space alignment                        & TRUE                                           \\
Color error cost                             & 3                                              \\
Auto-detect paired distances                 & TRUE                                           \\
Non-specific match handling                  & Map randomly                                   \\
                                             &                                                \\
\multicolumn{2}{l}{Find Best Matches using K-mer Spectra}                                     \\
References                                   & NCBI references (2017-07-08)                   \\
K-mer length                                 & 16                                             \\
Only index k-mers with prefix                & ATGAC                                          \\
Check for low quality and contamination      & TRUE                                           \\
Fraction of unmapped reads for quality check & 0.1                                            \\
                                             &                                                \\
De Novo Assembly                             &                                                \\
Mapping mode                                 & Create simple contig sequences (fast)          \\
Update contigs                               & TRUE                                           \\
Mismatch cost                                & 2                                              \\
Insertion cost                               & 3                                              \\
Deletion cost                                & 3                                              \\
Colorspace error cost                        & 3                                              \\
Length fraction                              & 0.5                                            \\
Similarity fraction                          & 0.8                                            \\
Colorspace alignment                         & TRUE                                           \\
Alignment mode                               & local                                          \\
Match mode                                   & random                                         \\
Create list of un-mapped reads               & FALSE                                          \\
Automatic bubble size                        & TRUE                                           \\
Bubble size                                  & 50                                             \\
Automatic word size                          & TRUE                                           \\
Word size                                    & 20                                             \\
Minimum contig length                        & 200                                            \\
Guidance only reads                          &                                                \\
Perform scaffolding                          & TRUE                                           \\
Auto-detect paired distances                 & TRUE                                           \\
Create report                                & TRUE                                           \\
                                             &                                                \\
\multicolumn{2}{l}{Find Resistance}                                                           \\
DB                                           & Database for Find Resistance (2018-02-02)      \\
Minimum identity \%                          & 70                                             \\
Minimum length \%                            & 20                                             \\
Filter overlaps                              & TRUE                                           \\
Local Realignment                            &                                                \\
Realign unaligned ends                       & TRUE                                           \\
Multi-pass realignment                       & 2                                              \\
Guidance-variant track                       &                                                \\
Maximum guidance-variant length              & 100                                            \\
Force realignment to guidance-variants       & FALSE                                          \\
                                             &                                                \\
InDels and Structural Variants (2)           &                                                \\
P-Value threshold                            & 1.00E-04                                       \\
Maximum number of mismatches                 & 3                                              \\
Ignore broken pairs                          & TRUE                                           \\
Filter variants                              & FALSE                                          \\
Minimum number of reads                      & 2                                              \\
Minimum relative consensus coverage          & 0                                              \\
Minimum quality score                        & 0                                              \\
Restrict calling to target regions           &                                                \\
                                             &                                                \\
Local Realignment (2)                        &                                                \\
Realign unaligned ends                       & TRUE                                           \\
Multi-pass realignment                       & 2                                              \\
Guidance-variant track                       & Defined by: InDels and Structural Variants (2) \\
Maximum guidance-variant length              & 100                                            \\
Force realignment to guidance-variants       & FALSE                                          \\
                                             &                                                \\
\multicolumn{2}{l}{Identify MLST Scheme from Genomes}                                         \\
Schemes                                      & PubMLST (04-03-2017)                           \\
                                             &                                                \\
Identify MLST                                &                                                \\
Scheme                                       & Defined by: Identify MLST Scheme from Genomes  \\
Low coverage reported when below             &                                               
\end{longtable}
